---
title: Week 6 - Centrality and Centralization
sort: 6
format: 
  revealjs:
    css: /resources/custom_css.css
    theme: white
    progress: true
    transition: convex
    reveal_plugins: ['notes']
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = './')
source("resources/preamble.R")
library(tidygraph)
library(ggraph)
```

## Dad Joke

Can you believe my wife told me to quit acting like a flamingo?

<p class='fragment'>
I had to put my foot down.
</p>

## Housekeeping

> - Homework questions in #homework-help on Discord
>	- How to copy and paste code


<!--
## Collective Norms Discussion

> - I think our in-person conversations could be better
> - Too many tech distractions
> - Coming prepared
> - How to have more natural conversations?
-->


## Concept Review

> - What is centrality?
> - What is the difference between centrality and centralization?
> - What is degree centrality?
> - What are some shortcomings of degree centrality as a measure of power/influence?
> - What is betweenness centrality?
> - What is closeness centrality?
> - What is eigenvector centrality?

## Concept Review

> - What aspects of power/influence do centrality measures miss?
> - What can centralization tell us about a network?
> - What does density tell us about a network?
> - What is hierarchy?

## Practical Review

What is the degree/closeness/betweenness centrality of node A?

```{r echo=FALSE}
G <- play_gnp(6, 0.5, directed=F) |> as_tbl_graph() |>
  mutate(name = LETTERS[1:nrow(.N())])


G |>
  # Get first N letters of alphabet
  ggraph(layout = 'stress') +
  geom_edge_fan() +
  #geom_node_point(aes(size = centrality_degree())) +
  geom_node_label(aes(label = name), size = 8) +
  theme_graph()
```

## Practical Review

What is the degree/closeness/betweenness centrality of node A?

```{r}
G |>
  mutate(degree = centrality_degree(),
         closeness = centrality_closeness(),
         betweenness = centrality_betweenness()) |>
  filter(name == "A")

```


## Discussion Questions


## R Review

